\documentclass[10pt]{article}

% ----------------------------------------------------------- essential packages
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
%\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{booktabs} % somewhat essential, I guess
\usepackage{setspace} % for double spacing, etc.
\usepackage{multicol} % multiple columns
\usepackage{tabularx} % tabularx

% ------------------------------------------------------------------- font stuff
%\renewcommand{\rmdefault}{ptm}
\renewcommand{\rmdefault}{ppl}
%\usepackage[urw-garamond]{mathdesign}
%\usepackage[T1]{fontenc}
%\usepackage[lite,zswash,eucal]{mtpro2}

% ----------------------------------------------------------- fancy header stuff
\usepackage{fancyhdr}
%\pagestyle{fancy}
%\fancyhead[LO,LE]{}
%\chead{\textbf{Algebra}}
%\fancyhead[RO,RE]{}

\setlength{\parindent}{0pt}
\setlength{\parskip}{.75em}

% -------------------------------------------------------------- hyperlink stuff
\usepackage{hyperref}
\hypersetup{colorlinks=true,urlcolor=blue}

% ------------------------------------------------------------------- tikz stuff
\usepackage{tikz}
\tikzset{%
  every picture/.style={thick, >=stealth}%
}
\usetikzlibrary{positioning}
%\usetikzlibrary{decorations.markings}

% ----------------------------------------------------------------------- macros
\newcommand{\sect}[1]{
\vspace{.75em}
\textbf{\textsc{\Large #1}}

\vspace{-1.5em}
\noindent\rule{\textwidth}{.5pt}
\vspace{-1.5em}
}
\newcommand{\CC}{\mathbf{C}}
\newcommand{\RR}{\mathbf{R}}
\newcommand{\QQ}{\mathbf{Q}}
\newcommand{\ZZ}{\mathbf{Z}}
\newcommand{\NN}{\mathbf{N}}
\DeclareMathOperator{\id}{id}

% --------------------------------------------------------------- begin document
\begin{document}

\thispagestyle{empty} % removes page number from first page

\begin{tabularx}{\textwidth}{@{}X >{\centering}X X@{}}
  \emph{\large Curriculum Vit\ae} &
  \textbf{\textsc{\huge Chester Lian}} &
  \hfill\emph{\large September 2017}
\end{tabularx}

\vspace{-1em}
\rule{\textwidth}{1pt}
%\vspace{-1.5em}

\begin{center}
\begin{tabular}{rl}
\textbf{Address} &
Mathematics Department, Duke University, Box 90320, Durham, NC 27708-0320 \\
\textbf{E-mail} & \href{mailto:chester@math.duke.edu}{\texttt{chester@math.duke.edu}} \\
\textbf{Website} &
\href{http://math.duke.edu/\~chester}{\texttt{http://math.duke.edu/\textasciitilde
chester}} \\
\textbf{Citizenship} & Malaysia
\end{tabular}
\end{center}
\vspace{-1em}

\sect{Education}

\textbf{Duke University}, Durham, NC \hfill 2013--present \\
Ph.D.\ candidate in Mathematics \\
Advisor: Lenhard Ng

\textbf{University of Dayton}, Dayton, OH \hfill 2009--2013 \\
B.S. (Honors with Distinction) in Mathematics and Computer Science, summa cum
laude \\
Honors thesis: An Aronszajn Tree \\
Minor: Philosophy

\sect{Research interests}

Low-dimensional topology, knot theory, contact topology, symplectic topology

\sect{Publications}

\vspace{-1em}
\begin{enumerate}

  \item On the Decompositions of Complete Graphs into Cycles and Stars on the
  Same Number of Edges (with A. Abueida). \emph{Discussiones
  Mathematicae Graph Theory} 34.1 (2014), 113--125.

\end{enumerate}
\vspace{-1em}

\sect{Talks}

\setlength{\leftskip}{1em}

\emph{An Aronszajn Tree.} Brother Joseph W.\ Stander Symposium, University of
Dayton, April 2013.

\emph{Decompositions of Complete Graphs into Cycles and Stars on the Same Number
of Edges.} Undergraduate Mathematics Day, University of Dayton, November 2011.

\emph{Decompositions of Complete Graphs into Cycles and Stars on the Same Number
of Edges.} Brother Joseph W.\ Stander Symposium, University of Dayton, April
2011.

\setlength{\leftskip}{0em}

\vspace{.5em}
\textbf{\textsc{\large Seminars and Colloquia}}
\vspace{-.25em}

\setlength{\leftskip}{1em}

\emph{On the Heegaard Floer Homology of Branched Double-covers.} Heegaard Floer
Homology Summer Seminar, North Carolina State University, August 2017.

\emph{Moser's Trick in Symplectic Geometry and Morse Theory.} Geometry and
Topology Graduate Seminar, Duke University, November 2016.

\emph{Morse Homology.} Topology Learning Seminar, North Carolina State
University, September 2016.

\emph{Group Theory in Practice: Solving a Rubik's Cube Blindfolded.} Department
Colloquium, University of Dayton, December 2011.

\setlength{\leftskip}{0em}

\sect{Conferences}

Georgia International Topology Conference, Georgia Tech, Athens, GA \hfill May
2017\setlength{\parskip}{.25em}

Triangle Area Graduate Mathematics Conference (TAGMaC), Duke, Durham, NC \hfill
March 2017

AMS Fall Southeastern Sectional Meeting, NCSU, Raleigh, NC \hfill November 2016

Knots in the Triangle, NCSU, Raleigh, NC \hfill April 2016%
\setlength{\parskip}{.75em}

\newpage
\sect{Awards and Honors}

\textbf{Captain L.\ P.\ and Barbara Smith Award for Teaching
Excellence} \hfill Academic year 2016--2017\setlength{\parskip}{.25em}

\textbf{Captain L.\ P.\ and Barbara Smith Award for Teaching
Excellence} \hfill Academic year 2015--2016

\textbf{Trustees' Scholarship}, University of Dayton (full-tuition
scholarship) \hfill 2009--2013

%Highest scholarship awarded by the University of Dayton: four years tuition, two
%years room and board

\textbf{University Honors Program}, University of Dayton \hfill
2009--2013

\textbf{Pi Mu Epsilon}, National Mathematics Honorary Society \hfill
Inducted 2011\setlength{\parskip}{.75em}

\sect{Teaching}

\textbf{\textsc{\large Duke University}}

\setlength{\leftskip}{1em}

\vspace{-.25em}
\textbf{Instructor of Record}
\setlength{\parskip}{.25em}

Math 105L, Laboratory Calculus and Functions I \hfill Fall 2014

Math 111L, Laboratory Calculus I \hfill Fall 2015

Math 112L, Laboratory Calculus II \hfill Spring 2016, Spring 2017

Math 771S, Teaching College Mathematics (co-instructor: Emily Braley) \hfill
Fall 2016\setlength{\parskip}{.75em}

\textbf{Lab Instructor}
\setlength{\parskip}{.25em}

Math 111L, Laboratory Calculus I \hfill Fall 2013\setlength{\parskip}{.75em}

\setlength{\leftskip}{0em}

\vspace{.5em}
\textbf{\textsc{\large University of Dayton}}

\setlength{\leftskip}{1em}

\vspace{-.25em}
\textbf{Supplemental Instruction Leader}
\setlength{\parskip}{.25em}

MTH 218, Analytic Geometry and Calculus III \hfill Fall 2010\setlength{\parskip}{.75em}

\textbf{Teaching Assistant}
\setlength{\parskip}{.25em}

MTH 137, Calculus I with Review \hfill Fall 2012

MTH 168, Analytic Geometry and Calculus I \hfill Fall 2011, Spring 2012

MTH 169, Analytic Geometry and Calculus II \hfill Spring
2011\setlength{\parskip}{.75em}

\textbf{Grader}
\setlength{\parskip}{.25em}

MTH 310, Linear Algebra and Matrices \hfill Spring 2010\setlength{\parskip}{.75em}

\setlength{\leftskip}{0em}

\sect{Languages}

English (native), Mandarin Chinese (native), Cantonese (native), Malay (native),
German (limited working proficiency)

\end{document}
